Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-14 introduction.tex
updated abstract

Backscatter enables wireless communication at orders of magnitude lower
energy cost than traditional radios. A backscatter transmitter operates
by either reflecting or absorbing existing wireless signals, which only
incurrs in very low power consumption in the order of
micro-Watts~\cite{liu_ambient_2013}. As a consequence backscatter
communication is emerging as the mechanism of choice to network
battery-free devices.  Over the past few years significant progress has
been made to make backscatter communication practical for Internet of
Things~(IoT) devices. Early backscatter systems, like RFID, required a
dedicated device to generate the necessary carrier to be backscattered.
State-of-the-art systems, however, reflect ambient WiFi or television
signals~\cite{liu_ambient_2013} instead, which does away with the need for
dedicated infrastructure.

>>>>

Backscatter communication enables wireless transmissions
at energy consumption which is several orders of magnitude
lower than traditional radios. Backscatter achieves ultra-low
power wireless transmissions by reflecting or absorbing ambient
wireless signals, which as an operation consumes only 
\SI{}{\micro\watt}s of power consumption~\cite{liu_ambient_2013}. 
As a consequence backscatter
communication is emerging as the mechanism of choice to network
devices operating on harvested energy.  
Over the past few years there has been significant progress
to make backscatter a viable mechanism to network Internet of
Things~(IoT) devices. Early backscatter systems, like RFID readers, required a
dedicated device to generate the necessary carrier signal, which were later
reflected by the tags. On the other hand, recent state-of-the art systems 
does away the need for a dedicated device to generate carrier signals. 
Recent systems can leverage either already deployed infrastructure of
devices to generate carrier signal, or leverage ambient WiFi or TV
signals~\cite{liu_ambient_2013}.
